1 Report ASP20 Boost

### 2020-05-27 Reports/1_REPORT.Rmd
Ammend to last commit text: - Included short tutorial to use Rmd for academic wrtiting (with references). - Set the outline for first report. - Set "report" folder including all relevant files for compiling + R Studio Rmd cheatsheets.
- Reformated outline - Expanded the introduction.

# How to cite and configure the document's appearance

@@

In the `report` folder there's two `.bib` files. 
These contain all reference we should need. 
To update the `package.bib` write the name of the package in the following chunk and *actively* run it (It should be installed in your terminal).

@@

# 0.Lead Questions to be answered (from Hannes' e-mail):

* Which open questions do you have about the statistical model and methodology?
*  What functionality are you planning to (or did you already) implement? What did you decide to leave out?
* What are the critical aspects of your implementation and your package? Stability? Performance? User-friendliness? How are you going to deal with these potential issues?
    What design designs did you make with respect to your implementation? How are you going to extend the R6 class? What additional functions are you going to provide?

# 1. Description of the problem

We have been working on an implementation for a boosting implementation with gradient descent for location and scale.

@@

## Johannes is gzus.

# 3. Intended extensions to be implemented. 
# 4. Comments
# 5. References

>>>>

# How to cite and configure the document's appearance 
If you don't have Latex download latex for R with `tinytex::install_tinytex()`.

@@

In the `report` folder there's two `.bib` files. 
These contain all reference we should need. 
To update the `package.bib` write the name of the package in the following chunk and *actively* run it (It should be installed in your terminal).
The`citavi.bib` file needs to be exported from citavi.

@@

# 1. Introduction:

* The developement of this package takes place in the framework of the seminar "Advanced Statisical Programming" -> SS20
* We expand the R6 class *"LocationScaleRegression"* belonging to the `asp20model` package concieved specifficaly for this seminar [@R-asp20model]
* Our aim is to develope an multi-faceted implementation of boosting for location and scale including component-wise boosting, use of cross-validation to determine the optimal stopping critera  and useful options for visualization.

@@

> Hannes lead question: What are the critical aspects of your implementation and your package? Stability? Performance? User-friendliness? How are you going to deal with these potential issues?

> 2. What design designs did you make with respect to your implementation? How are you going to extend the R6 class? What additional functions are you going to provide?

I propose a timeline where the implementation process is described step by step as a list e.g:

1. Primitive implementation of boosting
2. Simple boosting for location implemented
3. Adressed the estimation for the variance of gamma. 
4. Johannes finished everything #lol. 27.05.

## Johannes is *gzus*.

# 3. Description of the problem

> Hannes lead question: Which open questions do you have about the statistical model and methodology?

# 4. Extensions to be implemented.

> Hannes' Lead question: What functionality are you planning to (or did you already) implement? What did you decide to leave out?

# 5. Summary?
# 6. References

### 2020-05-27 Reports/1_REPORT.tex
- Reformated outline - Expanded the introduction.

@@

In the \texttt{report} folder there's two \texttt{.bib} files. These
contain all reference we should need. To update the \texttt{package.bib}
write the name of the package in the following chunk and \emph{actively}
run it (It should be installed in your terminal).

@@

\hypertarget{lead-questions-to-be-answered-from-hannes-e-mail}{%
\chapter{0.Lead Questions to be answered (from Hannes'
e-mail):}\label{lead-questions-to-be-answered-from-hannes-e-mail}}

\begin{itemize}
\tightlist
\item
  Which open questions do you have about the statistical model and
  methodology?
\item
  What functionality are you planning to (or did you already) implement?
  What did you decide to leave out?
\item
  What are the critical aspects of your implementation and your package?
  Stability? Performance? User-friendliness? How are you going to deal
  with these potential issues? What design designs did you make with
  respect to your implementation? How are you going to extend the R6
  class? What additional functions are you going to provide?
\end{itemize}

\hypertarget{description-of-the-problem}{%
\chapter{1. Description of the
problem}\label{description-of-the-problem}}

We have been working on an implementation for a boosting implementation
with gradient descent for location and scale.

@@

\hypertarget{johannes-is-gzus.}{%
\section{Johannes is gzus.}\label{johannes-is-gzus.}}

\hypertarget{intended-extensions-to-be-implemented.}{%
\chapter{3. Intended extensions to be
implemented.}\label{intended-extensions-to-be-implemented.}}

\hypertarget{comments}{%
\chapter{4. Comments}\label{comments}}

\hypertarget{references}{%
\chapter*{5. References}\label{references}}
\addcontentsline{toc}{chapter}{5. References}

>>>>

If you don't have Latex download latex for R with
\texttt{tinytex::install\_tinytex()}.

@@

In the \texttt{report} folder there's two \texttt{.bib} files. These
contain all reference we should need. To update the \texttt{package.bib}
write the name of the package in the following chunk and \emph{actively}
run it (It should be installed in your terminal). The\texttt{citavi.bib}
file needs to be exported from citavi.

@@

\hypertarget{introduction}{%
\chapter{1. Introduction:}\label{introduction}}

\begin{itemize}
\tightlist
\item
  The developement of this package takes place in the framework of the
  seminar ``Advanced Statisical Programming'' -\textgreater{} SS20
\item
  We expand the R6 class \emph{``LocationScaleRegression''} belonging to
  the \texttt{asp20model} package concieved specifficaly for this
  seminar (Riebl 2020)
\item
  Our aim is to develope an multi-faceted implementation of boosting for
  location and scale including component-wise boosting, use of
  cross-validation to determine the optimal stopping critera and useful
  options for visualization.
\end{itemize}

@@

\begin{quote}
Hannes lead question: What are the critical aspects of your
implementation and your package? Stability? Performance?
User-friendliness? How are you going to deal with these potential
issues?
\end{quote}

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  What design designs did you make with respect to your implementation?
  How are you going to extend the R6 class? What additional functions
  are you going to provide?
\end{enumerate}
\end{quote}

I propose a timeline where the implementation process is described step
by step as a list e.g:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Primitive implementation of boosting
\item
  Simple boosting for location implemented
\item
  Adressed the estimation for the variance of gamma.
\item
  Johannes finished everything \#lol. 27.05.
\end{enumerate}

\hypertarget{johannes-is-gzus.}{%
\section{\texorpdfstring{Johannes is
\emph{gzus}.}{Johannes is gzus.}}\label{johannes-is-gzus.}}

\hypertarget{description-of-the-problem}{%
\chapter{3. Description of the
problem}\label{description-of-the-problem}}

\begin{quote}
Hannes lead question: Which open questions do you have about the
statistical model and methodology?
\end{quote}

\hypertarget{extensions-to-be-implemented.}{%
\chapter{4. Extensions to be
implemented.}\label{extensions-to-be-implemented.}}

\begin{quote}
Hannes' Lead question: What functionality are you planning to (or did
you already) implement? What did you decide to leave out?
\end{quote}

\hypertarget{summary}{%
\chapter{5. Summary?}\label{summary}}

\hypertarget{references}{%
\chapter*{6. References}\label{references}}
\addcontentsline{toc}{chapter}{6. References}
